---
title: "Forecasting Covid-19 in the US"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This repo is set up to contribute to the [Covid-19 Forecast Hub](https://github.com/reichlab/covid19-forecast-hub), which is hosted by [Reich Lab](https://reichlab.io/covid19-forecast-hub/).

## Methods
We use an ensemble of models to forecast deaths from Covid-19 in US states. These include:
- Rt estimation: [code](https://github.com/epiforecasts/covid-us-forecasts/tree/master/rt-forecast), relying on methods developed in [EpiNow](https://epiforecasts.io/EpiNow/)
- Time-series: [code](https://github.com/epiforecasts/covid-us-forecasts/tree/master/timeseries-forecast) in progress

We [output](https://github.com/epiforecasts/covid-us-forecasts/tree/master/death-forecast) 1 to 4 week ahead forecasts of weekly cumulative and incident deaths, for the US and selected US states. See the [project board](https://github.com/epiforecasts/covid-us-forecasts/projects) for ongoing work.

For national and sub-national Rt estimates and forecasts in other countries, see our [website](https://epiforecasts.io/covid/posts/global/).

## Development
Please add an issue if you would to get in touch or contribute.
##### Contributors
LSHTM, Centre for Mathematical Modelling of Infectious Disease:
- Sam Abbott (@seabbs)
- Sophie Meakin (@sophiemeakin)
- Kath Sherratt (@kathsherratt)
- Nikos Bosse (@nikosbosse)
- Sebastian Funk (@sbfnk) and [Epiforecasts](https://github.com/epiforecasts) team



```{r eval=FALSE}



```
